% NSF proposal generation template style file.
% based on latex stylefiles written by Stefan Llewellyn Smith and
% Sarah Gille, with contributions from other collaborators.
%
\documentclass{proposalnsf}

% See this file for a set of pre-defined journal abbreviations
\input{journal-abbreviations.tex} 
\usepackage{hyperref}
\usepackage{xcolor}

\newcommand{\keyword}[2]

\newcommand{\degrees}{$\!\!$\char23$\!$}
\newcommand{\armin}[1]{\colorbox{cyan}{#1}}
\newcommand{\austin}[1]{\colorbox{yellow}{#1}}
\newcommand{\greg}[1]{\colorbox{orange}{#1}}
\newcommand{\josh}[1]{\colorbox{green}{#1}}
\newcommand{\red}[1]{\colorbox{red}{#1}}
\newcommand{\ana}[1]{\colorbox{red}{#1}}
\newcommand{\changeit}[1]{\colorbox{magenta}{#1}}

\newcommand{\eg}{\emph{e.g.}}
\newcommand{\id}{\emph{i.d.}}

\renewcommand{\refname}{\centerline{References cited}}

% This handles hanging indents for publications
\def\rrr#1\\{\par
\medskip\hbox{\vbox{\parindent=2em\hsize=6.12in
\hangindent=4em\hangafter=1#1}}}

\def\baselinestretch{1}

\begin{document}
{\LARGE{
\noindent
\armin{Armin please review}\\
\austin{Austin please review}\\
\greg{Greg please review}\\
\josh{Josh please review}\\
\ana{Ana please review}\\
\changeit{To be changed}}}

\clearpage
\begin{center}
{\Large{\bf Project Summary}}\\*[3mm]
{\bf AI detecting reflections in the LSST data} \\*[3mm]

Federica B.  Bianco, PI; 
Austin J.  Brockmeier, 
Armin Rest, CoIs; \\
Gregory Dobler, 
Joshua Peek, Collaborators
\end{center}

\noindent
{\bf Intellectual Merit} The Large Synoptic Survey Telescope (LSST) is the US flagship astronomical project of the 2020s.   LSST will conduct a 10-year survey generating an unprecedented amount of information-dense data: 20Tb/night, every night, for 10 years, pushing the envelope of big-data and data-science.   Observing the whole southern sky every few days, the LSST data reduction software will detect tens of thousands of changes in the sky every night, from transiting planets to exploding stars, but it will entirely miss \emph{light echoes}: the reflection of stellar explosions that light up the cosmic dust.   The detection of all-sky samples of light echoes (LEs) enables the reconstruction of the history of explosion of stars in our Galaxy, including the potential to detect an unknown galactic supernova, and the tracing of the Milky Way dust structure, which informs the evolution history of the Galaxy and improve inferences on extragalactic sources by constraining extinction.  However, LEs are faint, rare, and diffuse features that change over time, and are hard to detect.  Presently, no automated pipeline for this task exists.  LSST will observe the entire southern sky at $\sim$day time intervals and with high sensitivity and spatial resolution, making it the ideal survey to detect LEs.  This program will support the development of the first pipeline for the automated all-sky detection of LEs by leveraging cutting edge artificial intelligence techniques and its deployment on the LSST computing platform.  The products of this work will be primarily three: (1) a method to detect LEs in all sky images optimized for LSST and implemented on the LSST platform as a User-Generated data product. (2) A census of LEs on the Galaxies which will be combined with eruption and explosion models to constrain the history of eruption and explosion of the Milky Way. (3) A method to generate detailed, spatially resolved dust maps automatically in correspondence to any light echoes detected in all-sky surveys.

\medskip

\noindent
{\bf Broader Impacts}
The broader impact of this proposal will leverage the fascinating phenomenon of LEs to develop data science skills.  It will provide research and training opportunities for graduate and undergraduate students.  The involvement of CoI Brockmeier (Professor of Electrical and Computer Engineering), and the connection of PI Bianco, CoI Brockmeier, and Collaborator Dobler with the new UD Data Science Institute will provide an immersive environment where our students can benefit from mentoring opportunities, as well as opportunities to share their work on a regular basis (\eg  Data Science Symposia\footnote{\url{https://dsi.udel.edu/dsi-symposium-2019/}}).   Furthermore, the CoIs will develop a hackathon program for University of Delaware students.  This will provide prime active learning experiences, a unique venue to get involved in data science and with opportunities to prototype solutions for LSST data analysis, but not limited to LSST, and even astrophysics, offering data science projects across disciplines.  This learning environment is ideal to develop superskills not generally offered in the classroom or even in traditional research projects: from project scoping and design, to collaborative and communication skills.
\renewcommand{\thepage} {B--\arabic{page}}

%\newpage

% reset page numbering to 1.   This is helpful, since the text can only
% be 15 pages, and reviewers will want to believe we've kept within
% those limits

\pagenumbering{arabic}
\renewcommand{\thepage} {D--\arabic{page}}

\newpage

\centerline{\bf Results from Prior NSF Support}

\noindent
{\bf Previous Award Title}
{\it award number} (PI); dates, \$amount

Research carried out ....

\ \\

\noindent{\Large \bf PROJECT DESCRIPTION}

\section{Introduction}


About a century ago a true paradigm shift happened in astronomy.   The introduction of digital equipment enabled the discovery and study of the “transients and variable sky” : the sky that in all human mythologies was assumed to be never-changing came to life with the detection of energetic phenomena happening every instant: 10 stars explode every second [a], stars merge deforming space-time in gravitational waves [a], they erupt [a], and more.   A century ago seeing an astronomical transient was a once-in-a-lifetime event, now we see many-a-day, and yet we have barely scratched the surface of this scientific opportunity.  Until now, astronomical surveys were limited in either depth, only enabling the observation of the closest and brightest transients, area, observing small regions of sky, or resolution.   Today we can detect ~100 transients each night [4].   LSST will detect tens of thousands, representing not an incremental, but a transformational change.  

{\bf The LSST project} includes the construction of a telescope and a 10-year survey to begin in 2022 [5].  LSST will deliver an unprecedented volume of information-dense data (20Tb/night) with the potential to revolutionize nearly all astrophysics domains [6], from revealing the smallest bodies in the Solar System, to measuring the rate of expansion of the Universe.   LSST will photograph the sky at resolution and depth comparable to those of the Hubble Space Telescope, but unlike previous surveys, limited to small regions, it will deliver observations at a few days’ cadence over the whole southern sky.   This will truly open a window into the transient Universe.  

{\bf Light Echoes} (LEs) are the reflection of stellar explosions on interstellar dust.  They appear in the sky as diffuse transients: faint, extended, time-varying [7].  
As part of its federally funded operations, LSST will produce $10^6$ nightly alerts, each one announcing a changing or moving source (stars, asteroids, etc).   It will detect thousands of transients and variable “point sources” in each image but these diffuse features will be entirely missed.   LEs help characterize stellar explosions by offering the view of an explosion from different lines of sight, a unique opportunity in astrophysics [8,9] 
 and allowing us to revisit events even when the transient was originally not detected [10].  
{\bf\emph{ The detection of LEs across a large portion of the sky enables the reconstruction of the history of stellar explosions of our Galaxy, the potential to detect an unknown galactic supernova, and the tracing of the Milky Way dust structure, which will inform the evolutionary history of the Galaxy and improve inference on extragalactic sources by constraining extinction.  }}


{\bf However, LEs are extremely hard to detect}, and, to date, they are still discovered by visual inspection, a method that obviously does not scale to the LSST data volume.   Even crowd-sourcing cannot help this science in the LSST era: simple scaling from the Galaxy Zoo \ana{[CITE]} project indicates that the entire population of the Earth would be insufficient to study the full dataset using the same methods.   We propose to leverage Artificial Intelligence to address this low signal-to-noise regime computer-vision challenge and create the first pipeline for automated detection of LEs.   {\bf \emph{This will allow us to use images from the LSST survey to produce a census of LEs that would constrain the history of Milky Way stellar explosions.   The two-year timeline of this proposal aligns perfectly with LSST, with the first commissioning data expected in 2021 and the survey begin observing in late 2022}}.






\section{\armin{ Light Echoes phenomenology and significance}}
LEs are the reflections light from astrophysical trasients off interstellar dust in their surroundings.   As the light from a transient propagates into space, it may be reflected towards Earth, and our telescopes, if it encounters a sheet of interstellar dust.  The geometry of LEs is straightforward, a transient and the Earth are at two focal points of a 3D ellipsoid; light from the transient reflected off dust that intersects the same ellipsoid surface reaches Earth at the same time.  As time goes by, the ellipsoidal surface expands.  Due to the extra travel time, a light echo reaches the observer at a later time than the light directly detected from its source.

LEs appear as faint, extended, time-changing features in the sky.  The complexity of their shape is inferred by the complexity of the underlying dust structure, while the time-changing aspect is due to the traveling of light across the dust sheet.

LEs provide unique insight into the transients that originated them and the dust that produced them.  
\subsection {Nature of the transient}
The nature of transients can be studied in detail in their LEs: this technique has enabled the characterization of historical supernovae with modern instrumentation [8,19,20].  When historical transients are observed (again) today in LEs, they can be studies with modern observing techniques: large telescoped (that can compensate for the factor $10$ decrease in brightness and), digital cameras, and,most importantly, spectrographs that enable typing and the characterization of physical properties of the transient that cannot be inferred from overall magnitude measurements.  For examples: the historic Tycho supernova, was first observed in northern Europe in 1572.  At the time, the concept of stars having a finite life-time was many years to come.  When re-detected in 20??, a study lead by CoI Rest identified the explosion as a supernova of type Ia (SNIa), through the analysis of the spectral features of the LE.  These studies 
require a sophisticated modeling of the dust reflection effects to deconvolve the imprint of the dust from the spectrum of the transient (or rather, to convolve the spectra of directly observed transients with a kernel reproducing the effects of dust and enable comparisons).  CoI Rest is the foremost world expert in this technique \citep{rest11a}.

A blooming field of LEs, detected by our team in the surrounding of Eta Carinae, simply revolutionized our understanding of the nature of this transient, generating numerous publications and radically new models to explain the stellar eruption \changeit{[cite all Eracar including Owocki]}

\subsection{Asymmetry}
LEs, specifically the reflection of astronomical transients onto interstellar dust, enable the study of a transients from multiple lines of sight, a unique opportunity in astrophysics, allowing insight into the physical mechanism of stellar eruptions and explosions [3,8,9,19,20].  Cassiopea A (CasA) stands as a prime example of this: as for other supernova remnants, the remnant of CasA shows signs of asymmetry \changeit{[CITE]}.  But asymmetries in a remnant may be imprinted during the expansion of the ejecta.  CasA LEs, however, which are available from different lines of sight, have provided evidence that the explosion itself was asymmetric, a crucial piece of information to constrain explosion models.  Our team not only conducted the original study that detected the asymmetry signatures in spectra of CasA from different LEs \tochange[RESTCASA], but we also conducted subsequent studies that related the diversity in the sample of obswerved supernova IIb \tochange[Finn], the same type as CasA, to the asymmetry of CasA, demonstrating that the amount of asymmetry measured in CasA is itself comparable to the spectral diversity observed over N SNe IIb.

\subsection{Dust}
\armin{Armin can you add to this?}
The study of the dust structure that reflects the light allows us to characterize and study stellar eruptions through the characteristics of the ejection of material [21].

The iconic images of supergiant start V838 Monocerotis are the most astounding example of LEs revealing the dust structure around a variable\footnote{https://en.wikipedia.org/wiki/V838_Monocerotis}. 

LEs have been facilitated the study of \armin{[words words words]}

Of course, high signal-to-noise ratio LEs such as that one not the target of this proposal. With this proposal we aim at detecting faint light echoes, such that we can construct a and extracting info from a large sample, really the first statistical sample of LEs. 


\changeit{probably remove cause not relevant but cool:} Recently, LEs have been leveraged even to detect planets around low mass stars (\citep{sparks2018})

\subsection{What detection of LEs at scale enables}
All of these lines of inference are afforded by the study of individual LEs, but due to its sensitivity and all-sky observing strategy, LSST will for the first time enable observation of very faint phenomena on all-sky scale.  on the long term, the detection of LEs on a large scale across the entire sky will enable several science projects.

\begin{itemize}
  \item 
LEs may reveal unobserved Galactic supernovae.  
 \item 
LSST we expect to be able to do something unprecedented: build a census of Galactic LEs that will allow us to reconstruct the history of explosions and eruptions of the Milky Way, providing insight into the evolution of our Galaxy.   
\item Since all Galactic dust shines in reflected light, however faintly, the detection of LEs will also enable the study of the Galaxy dust structure on large scale.   In combination with studies of the structure from stellar extinction (its ability to absorb light [22]) this will provide an unprecedentedly detailed, three-dimensional map of the Galactic dust which will inform studies of Galaxy formation and improve the characterization of any observed extragalactic source.  
\end{itemize}

\section{\armin{The specific challenges in light echo detection}}


The astronomical community has very specific computer vision needs : common preprocessing tasks like rectifying, stitching, and bundling have been perfected for the low signal-to-noise sparse images that are the norm in astronomy.  Similarly, difference imaging and the detection of changes has seen development since the very early computational methods developed in the 1990s~\citep{alardlupton99} and, combined with machine learning tasks for increasing the purity of the detections~(\citealt{wozniak13} and most recently \citealt{duev19}).  With decades of experience in the study of astronomical transient in digital sky images, specialized software has been perfected to enable the discovery of astronomical transients to high sensitivity, even in real time.  This directly leads to the expectation that the LSST alert stream will be capable of delivering a stream of 10 million time-domain events per night, from transiting exoplanets, to gravitational microlensing, to the most distant explosions, every night, delivered within 60 seconds of closing the shutter.  Delivered to whom? To the entire world! for follow up and further investigation.  But this stream of alerts will miss LEs entirely.

The vast majority of astronomical transients are “point sources”, and detection software, including the LSST pipelines, are optimized for the detection of these point-source transients.



In addition, LEs are rare, or rather: LEs that are bright enough to be detected by present surveys, that are not as sensitive, or not as broad as LSST, are rare.  
{\bf LSST will usher a new era in the study of LEs by observing the entire hemisphere sky repeatedly at high spatial resolution and high sensitivity (limiting single-image depth magnitude g~24).  }

The detection of LEs is a difficult computer vision problem.   The problem is similar to the well-known, and notoriously difficult problem of detecting smoke-stacks and plumes, which PI Bianco also worked on in the context of Urban Science with a deep learning approach similar to the one proposed here (at the Urban Observatory [17]).  
The challenges include:
\begin{itemize}
  \item these features have diverse time-changing shapes, depending on the underlying dust structure and on the travel speed of the light across the dust (dominated by line-of-sight effects)
  \item reflections inside the telescope constitute a significant source of false positives, which cannot be disambiguated within a single image and requires time sequences to be analyzed.
  \item LEs appear as faint and diffuse features, ranging in luminosity until they blend into the image noise.   This problem is distinctly different from most image detection and recognition tasks, where the presence of the target object is unambiguous, and resolution is the most likely limiting factor.   
  \item the training set is limited: a few hundred examples.   This is a particular challenge in machine learning and artificial intelligence approaches.  


\end{itemize}
This proposal will support the development of an Artificial Intelligence (AI) model, a Generative Adversarial Neural Network [15], to detect LEs.   Deep Neural Networks and AI have recently been employed to solve astronomical tasks, primarily due to the rapid increase in data volume, which will culminate with the LSST survey and which requires scalable models that can efficiently extract information from Terabytes of data [\eg,  16].   Over the course of the next two years we expect to develop a model to detect LEs automatically in sky images and test the model on LSST precursor surveys.   Attempts to develop software to automatically detect LEs that are based on human-engineered features in images have not been successful, and by far the best method to detect LEs to date is human-inspection.  However, human-inspection obviously cannot scale to the volume of data generated by LSST and to the scope of the problem we ultimate propose to approach: the creation of a comprehensive census of Galactic LEs to study the history of stellar explosions and eruptions in the Milky Way.   

 This work will constitute a core portion of the PhD Thesis of one of PI Bianco’s graduate students at the DPA.   We will start from the limited size sample of real light-echo examples, a dataset of simulated LEs generated analytically, and images of the underlying dust wherever available (infrared observations of the sky reveal dust features, but high-resolution images are not available across the entire sky).   We will use successful Generative Adversarial Neural Networks designed to work under similar circumstances of limited-size real examples and simulated data [18].   Our team will retrain this network on light echo images from telescopes systems similar to the LSST (\eg,  from the Blanco telescope Dark Energy Camera, DES, images obtained in proposals co-authored by PI Bianco), and change the network architecture to suit our needs.  We expect to be able to test our model on real data as soon as commissioning data from LSST will become available.   In the meantime, our software can run on Blanco/DES images, that share many of the crucial characteristics of the LSST data but are not as sensitive to faint magnitudes, leading to a lower detection rate, looking for known and unknown LEs.


The two-year timeline of this proposal aligns perfectly with LSST, whose first commissioning data are expected in 2021 and which will begin observing in 2022.   The work to be conducted under this proposal will produce important software that will allow us to “hit the ground running” and begin detecting LEs in LSST images as soon as the LSST survey begins to produce data.  

\section{\armin{Light echo data}}
Over the course of several years, members of our team have collected hundreds of images of light echos.  Since 2010, the discovery of the LEs of Eta Carinae~\citep{Rest2019} lead to a hunt for echoes in this rich dust region, which truly blooms with echoes .  Even prior to this CoI Rest had engaged in search campaigns for LEs of historical transients including: Tycho, Cas A, 3 SNe Ia in the Large Magellanic Clouds, Eta Carinae, and SN 1987A, amounting to several hundred of images with LEs for about about 100 light echo groups.   

While this may seem like a large number, traditional Neural Networks (such as those tested in the ImageNet\footnote{\url{http://image-net.org/}} challenge several years ago) have been shown to require at least $\sim 1000$ representative images.

Even if the number of images were sufficient (perhaps after significant pre-processing augmentation such as cropping, rotating, reflecting) the diversity of LEs (and really of the underlying dust structure) is vast! And several, or even a few hundred light echo images (with several repeats of the same echo at different epochs) are not going to be sufficient to span the full diversity of this phenomena.  



\section{Forward modeling and training on synthetic data}\label{sec:fwm}


We have developed a method that can create realistic, data-driven simulated LEs.  The method uses real interstellar medium (ISM) data from 21-cm, neutral hydrogen (HI) data cubes.  21-cm is a powerful tool here, as we know that HI is well mixed with dust.  Further, in many cases velocity is a good proxy for dust (see \changeit{Tchernyshov & Peek 2017} for details).  With very high spatial resolution and spatial dynamic range data cubes available (\changein{Peek+ 2018, McClure-Griffiths+ 2015}) so we can emulate the high resolution imaging of PS1 \changeit{?} and similar surveys

If we consider a voxel in the HI data cube to be some intensity at a position RA, Dec, radial velocity ($\alpha$, $\delta$, $v$), we can define a plane such that 

$$1~=~A~*~\alpha~+~B~*~\delta~+~C~*~v$$

We then take all the pixels near this plane in the HI data cube and integrate them along the velocity dimension to create a plane-of-sky image, which we can scale to realistic light-echo amplitudes.  If we tip the plane at the right angle to velocity (i.e.  set the value of $C$ appropriately), we can mimic the way the LEs slice through distant space and create very realistic structures.  The data volume of these HI cubes is so large, and the number of possible values of $A$ and $B$ so variable, we can generate far more synthetic echoes than even the largest networks will need.  

\emph{Milestone 1} :

The first milestone of this project will be the design of a Deep Neural Network architecture able to trained on these synthetic images and tested on real sky images from the Dark Energy Camera that is scalable to the orders of magnitude larger dataset that LSST will generate starting in 2022. We note that this milestone, which is our starting point, overlaps with another NSF proposal lead by PI Rest: \armin{NSFXXXX}, but this is but the beginning of our exploitation of machine learning for the discovery of LEs. Our model well go from models able to explore 7,000 sq degree in 2-3 epochs, under development by CoI Rest's team, to nearly $\sim$100 epochs per filter over 18,000 square degrees. Well beyond the ability to keep humans in the loop. The entire dataset that constitutes the basis of the largest light echo exploration to date, namely the one developed under NSFXXX, will be collected by LSST in as little as XXX weeks by LSST.  
We will, however, leverage the results of \armin{NSFXXXX}, including LEs detected by this proposal into our training and testing sets.



However, learning from synthetic
images may induce significant biases.  Gaps between synthetic and real image distributions are impossible to ascertain.  Although the realism of the synthetic LEs produced as described above is sufficient to fool human detection (expert human detection by CoI Rest) systematic differences between the real and synthetic data would lead a network to overfit features that are characteristic of the synthetic images and fail to
generalize on real images.  \citep{Shrivastava_2017_CVPR}.  


\section{GANS for image processing and analysis}

More text.

\section{Proposed methodology}

More text.
\section{GANS with real and simulated images}

More text.

\section{GANS with real and dust images}

More text.

\section{A model to extract dust structure from LEs}



\section{Time Line and Management Plan}

\subsection{Our team}
PI Bianco is a new faculty member at the University of Delaware (UD) Physics and Astronomy Department and Biden School of Public Policy and Administration,  as well as a Resident Faculty member of the new UD Data Science Institute.

PI Bianco’s scientific expertise range from data science to data-driven inference in astronomical transients, from nearby Solar System [12] to distant Supernova explosions [13].   She works closely with the team building and scoping the LSST telescope and survey and represents the community working on LSST in various settings (\eg,  recently at the National Academy of Science Space Science Week, invited by the Committee on Astronomy and Astrophysics).  

Among the many transient phenomena in PI Bianco’s research portfolio, she has worked on LEs collaborating with CoI Rest leading the data collection and analysis at the Las Cumbres Observatory Global network, which contributed the majority of the image data analyzed in [3] and focusing on the extraction of lightcurves from LEs that supports the analysis of typing and spectral evolution [19, 20, 24]
and studies that relate diversity in transients to asymmetry as assessed from LEs.  Additionally, she is working on technically similar computer vision issues in the context of urban imaging at the Urban Observatory \changeit[CITE], a multi-city facility lead by Collaborator Dobler where urban environments are studied through imaging and techniques adapted from astronomy (i.e.  photometry, spectroscopy) developing methodology to detect of faint transient diffused feature generated by building HVAC system and other emissions \changeit[CITE].

\subsection{Collaborator Joshua Peek, STScI}
Collaborato Peek developed the forward modeling methodology for LEs and produced several simulations as described in~\autoref{sec:fwm}.  He will make his existing simulations available and coach students in the methodology to create a comprehensive training sample to be fed to our Neural Networks.  

\subsection{Collaborator Gregory Dobler, UDelaware}
Dobler has extensive experience modeling interstellar dust emission, absorption properties, and grain composition as well as the application of machine learning (including neural networks and deep learning algorithms) to ~PB-scale imaging data sets. He will participate in the effort to incorporate dust properties into the analysis and applying machine learning algorithms to simulated data.

\armin{PLEASE REVIEW}
Rest is a world-renowned expert in LEs, from detection to transient characterization.  He has lead several successfull programs devoted to the study of LEs, including current NSF program \armin{XXX}.  He also has lead the acquisition and analysis of light echo data used in this proposal \armin{NOAO PROPOSAL NUMBERS FOR DECAM IMAGES}.  In this project, he will supervise a Graduate student from John Hopkins University in year 1, as well as co-advising the UD Graduate students in developing a detailed work plan and set up the data access, ingestion, and manual labeling to create a standardized dataset of LEs over which the performance of our models will be measured.   

\austin{PLEASE REVIEW}
CoI Brockmeier is a new faculty member at the University of Delaware (UD) Electrical and Computer Engineering and, as well, a Resident Faculty member of the new UD Data Science Institute.  His expertise in signal processing range from hyperspectral to \changeit{FINISH}

\section{Summary: Significance of proposed work}

More text.

\subsection{Intellectual Merit}

More text.
\section{Unfunded Collaborators}

\subsection{CoI Armin Rest, STScI}




\subsection{Collaborator Joshua Peek, STScI}
Peek is an Associate Astronomer and the Data Science Mission Office Project Scientist at the Space Telescope Science Institute.  He developed the forward modeling methodology for LEs and produced several simulations as described in~\autoref{sec:fwm}.  He will make his existing simulations available and coach students in the methodology to create a comprehensive training sample to be fed to our GANs.  

\subsection{Collaborator Gregory Dobler, UDelaware}
Dobler is an Assistant Professor at the Department of Physics and Astronomy, Biden School of Public Policy and Administration, and Data Science Institute at the University of Delaware.   He has extensive experience modeling interstellar dust emission, absorption properties, and grain composition as well as the application of machine learning (including neural networks and deep learning algorithms) to ~PB-scale imaging data sets.   In this project he will participate in the effort to incorporate dust properties into the analysis and applying machine learning algorithms to simulated data, as well as co-supervising the graduate and undergraduate students.

\subsection{Broader Impacts}
\input{bi.tex}

\clearpage
\noindent{\Large \bf j Supplementary Material}
\clearpage
\section{Postdoctoral Mentoring Plan - 1 page}

\input{postdoc}

\clearpage


\newpage
\pagenumbering{arabic}
\renewcommand{\thepage} {E--\arabic{page}}

\bibliography{refs}
\bibliographystyle{jponew}

\newpage
\pagenumbering{arabic}
\renewcommand{\thepage} {G--\arabic{page}}
\noindent{\Large \bf BUDGET JUSTIFICATION}

\end{document}
